---
title: |
  | P/B Ratios And Future Residual Income: 
  | Accounting Reading Group - Assignment II \vspace{1cm}
author:
  - name: Ulf Brüggemann
    orcid: 0000-0002-9793-6600
    email: u.bruggemann@hu-berlin.de
    affiliations:
      - TRR 266 Accounting for Transparency
      - Humboldt-Universität zu Berlin
  - name: Fikir Worku Edossa
    orcid: 0009-0008-3607-4753
    email: fikir.worku.edossa@hu-berlin.de
    affiliations:
      - TRR 266 Accounting for Transparency
      - Humboldt-Universität zu Berlin
date: today
date-format: MMM D, YYYY [\vspace{1cm}]
abstract: |
  | The following short paper is demonstration on how to use open science tools in empirical accounting research. It demonstrates how one can reproduce the table from @P_2013. In doing so, it documents and discusses, the research design choices that were made and the variations between the original and the reproduced results. \vspace{1cm} 
  | \vspace{6cm}
bibliography: references.bib
biblio-style: apsr
format:
  pdf:
    documentclass: article
    number-sections: true
    toc: false
fig_caption: yes
fontsize: 11pt
ident: yes
always_allow_html: yes
header-includes:
  - \usepackage[nolists]{endfloat}    
  - \usepackage{setspace}\doublespacing
  - \setlength{\parindent}{4em}
  - \setlength{\parskip}{0em}
  - \usepackage[hang,flushmargin]{footmisc}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=24pt,font=bf}
  - \usepackage{array}
  - \usepackage{threeparttable}
  - \usepackage{adjustbox}
  - \usepackage{graphicx}
  - \usepackage{csquotes}
  - \usepackage[margin=1in]{geometry}
---


```{r}
#| echo: false
#| output: false

library(dplyr)
library(kableExtra)

load("../output/results.rda")


custom_format <- function(x) {
  if (is.na(x)) {
    return("")
  }
  formatted <- sprintf("%.3f", x)
  sub("^0", "", formatted)
}

```

\pagebreak



# Introduction

The following short paper illustrates how to use open science tools in empirical accounting research.

The paper presents details on a replication of a table that was published in the textbook by @P_2013. While the original table is based on data for the period 1965 to 1995, the replication uses data for the period 1996 to 2015. Other than that, the replication follows the research design by @P_2013 as much as possible with the data at hand.

The original table as well as the replicated table are shown below.


```{r}
#| echo: false
#| output: asis

penman_table <- penman_table %>%
  mutate(across(where(is.numeric), ~ sapply(.x, custom_format)))

kable(
  penman_table,
  "latex",
  booktabs = TRUE,
  linesep = "",
  caption = "Original table Penman 2013 - P/B Ratios And Future Residual Income"
) %>%
  kable_styling(latex_options = c("hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE)
```


```{r}
#| echo: false
#| output: asis

replication_results <- replication_results %>%
  mutate(across(where(is.numeric), ~ sapply(.x, custom_format)))

kable(
  replication_results,
  "latex",
  booktabs = TRUE,
  linesep = "",
  caption = "Replicated table - P/B Ratios And Future Residual Income"
) %>%
  kable_styling(latex_options = c("hold_position", "scale_down")) %>%
  row_spec(0, bold = TRUE)
```

# Research Design Choices

Our replication is based on two files that comprise data from Worldscope. While the first file focuses on static information at the company level (items: ISIN, company name and country where the company is domiciled), the second file contains panel data at the company-year level (items: ISIN, year, market value of equity, book value of equity and net income).

Following @P_2013, we focus our analysis on companies that are domiciled in the United States. 

In addition, we impose the following requirements:

- We require both the market value of equity (i.e., the numerator of the P/B ratio) and the book value of equity (i.e., the denominator of the P/B ratio) to be positive because non-positive P/B ratios are not economically meaningful. 

- We focus the analysis on the period 1996 to 2015 (as required in the task sheet).

- In computing the residual income, we assume a constant cost of equity of 10% (for simplicity).
Other than that, we follow @P_2013 by 

- computing the residual income for the current year (year 0) and the subsequent six years (year 1 to 6),

- assigning each company-year to one of 20 groups based on the P/B ratio (e.g., the first group includes company-years with the highest 5% of P/B ratios, while the bottom group includes those with the lowest 5%),

- computing and tabulating median statistics on the P/B ratio and current as well as future residual income for each P/B group.


# Results

The replicated table shows some similarities with the original table by @P_2013 in that median residual income for years 1 and 2 (a) is highest for the group of company-years with the highest P/B ratios and (b) decreases monotonically by P/B group. These findings are in line with valuation theory that predicts higher P/B ratios for companies that are expected to generate higher future residual income.

However, the patterns are less clear for years 3 to 6 in the replicated table (in particular for the group with the highest P/B ratios), which stands in contrast to @P_2013.

# Conclusion

The paper presents details on a replication of a table that relates current P/B ratios to current and future residual income. The original table by @P_2013 uses data for the period 1965 to 1995. In contrast, the replication focuses on the period 1996 to 2015.

The replication yields mixed results. While the relation between current P/B ratios and residual income in the near future is similar to that presented in the original table, residual income patterns in the more distant future cannot be replicated. 


\pagebreak

\setcounter{table}{0}
\renewcommand{\thetable}{\arabic{table}}

# References {-}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent