---
title: |
  | P/B Ratios And Future Residual Income: 
  | Accounting Reading Group - Assignment II \vspace{1cm}
authors:
  - name: Ulf Brüggemann
    orcid: 0000-0002-9793-6600
    email: u.bruggemann@hu-berlin.de
  - name: Fikir Worku Edossa
    orcid: 0009-0008-3607-4753
    email: fikir.worku.edossa@hu-berlin.de
institute: "TRR 266 Accounting for Transparency"
date: today
fontsize: "9pt"
pdf-engine: xelatex # pdflatex creates rastered fonts
bibliography: references.bib
biblio-style: apsr
format: 
  beamer:
    slide-level: 3
    number-sections: true
    toc: false
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \usepackage{adjustbox} # To adjust the table size
- \input{beamer_theme_trr266.sty}
---


```{r}
#| echo: false
#| output: false

library(dplyr)
library(kableExtra)

load("../output/results.rda")


custom_format <- function(x) {
  if (is.na(x)) {
    return("")
  }
  formatted <- sprintf("%.3f", x)
  sub("^0", "", formatted)
}

```

\pagebreak

# Introduction

The following short presentation illustrates how to use open science tools in empirical accounting research.

- A replication of a table by @P_2013.

- Original based on data for the period 1965 to 1995

- Replication uses data for the period 1996 to 2015.

- Replication follows the research design by @P_2013 as much as possible with the data at hand.


# Original Table

- The original table by @P_2013 relates current P/B ratios to current and future residual income.

```{r}
#| echo: false
#| output: asis

penman_table <- penman_table %>%
  mutate(across(where(is.numeric), ~ sapply(.x, custom_format)))

kable(
  penman_table,
  "latex",
  booktabs = TRUE,
  linesep = "",
  caption = "Original table Penman 2013 - P/B Ratios And Future Residual Income"
) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 5) %>%
  row_spec(0, bold = TRUE)
```

# Replicated Table

```{r}
#| echo: false
#| output: asis

replication_results <- replication_results %>%
  mutate(across(where(is.numeric), ~ sapply(.x, custom_format)))

kable(
  replication_results,
  "latex",
  booktabs = TRUE,
  linesep = "",
  caption = "Replicated table - P/B Ratios And Future Residual Income"
) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 6) %>%
  row_spec(0, bold = TRUE)
```



# Data

Two files that comprise data from Worldscope. 

- The first file focuses on static information at the company level (items: ISIN, company name and country where the company is domiciled)

- The second file contains panel data at the company-year level (items: ISIN, year, market value of equity, book value of equity and net income).


# Research Design Choices


Following @P_2013, we focus our analysis on companies that are domiciled in the United States. 

In addition, we impose the following requirements:

- We require both the market value of equity (i.e., the numerator of the P/B ratio) and the book value of equity (i.e., the denominator of the P/B ratio) to be positive because non-positive P/B ratios are not economically meaningful. 

- We focus the analysis on the period 1996 to 2015 (as required in the task sheet).

- In computing the residual income, we assume a constant cost of equity of 10% (for simplicity).
Other than that, we follow @P_2013 by 

- computing the residual income for the current year (year 0) and the subsequent six years (year 1 to 6),

- assigning each company-year to one of 20 groups based on the P/B ratio (e.g., the first group includes company-years with the highest 5% of P/B ratios, while the bottom group includes those with the lowest 5%),

- computing and tabulating median statistics on the P/B ratio and current as well as future residual income for each P/B group.


# Results

The replicated table shows some 

- Similarities with the original table by @P_2013 in that median residual income for years 1 and 2 (a) is highest for the group of company-years with the highest P/B ratios and (b) decreases monotonically by P/B group.

- These findings are in line with valuation theory that predicts higher P/B ratios for companies that are expected to generate higher future residual income.

- However, the patterns are less clear for years 3 to 6 in the replicated table (in particular for the group with the highest P/B ratios), which stands in contrast to @P_2013.

# Conclusion

- A replication of a table that relates current P/B ratios to current and future residual income.

- The original table by @P_2013 uses data for the period 1965 to 1995. In contrast, the replication focuses on the period 1996 to 2015.

- The replication yields mixed results.

- While the relation between current P/B ratios and residual income in the near future is similar to that presented in the original table, residual income patterns in the more distant future cannot be replicated. 


# References {-}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent